Write Up for Prachtical Machine Learning Assignement

**Goal**
Predict on test cases if the participants are performing barbell lifts correctly and incorrectly in 5 different ways (A-E).

**Data**
Accelerometers on the belt, forearm, arm, and dumbell of 6 participants that have been classified accordingly.


*Loading Libraries and Data*
```{r, echo=FALSE}
library(caret)
library(randomForest)

train<-read.csv("pml-training.csv")
test<-read.csv("pml-testing.csv")
```

*Variable Selection*
Looking at the data showed the most of the variables many empty fields or NA.
Also the index variable, username, timestamps, windows were not used.
The chose variables are listed in varsel.
Variable 160 is "classe" for the training set and problem_id for the test set.

```{r}
varsel=c(8:11,37:49,60:68,84:86,102,113:124,140,151:160)
train <-train[,varsel]
test <-test[,varsel]
```

K-fold crossvalidation was planed, but due to limitations of my hardware, only one split was made using 75% the training data for training the model and 25% for estimating the out of sample error.

```{r}
inTrain<-createDataPartition(y=train$classe, p=0.75, list=FALSE)
training<-train[inTrain,]
testing<-train[-inTrain,]
```


*Create RandomForest Model*

RandomForest Model was chose because two simpler approaches PLS and rpart trees did not result in very good out of sample errors.


```{r, cache=TRUE}
model = randomForest(classe ~ .,data = training,importance=TRUE)
```

*Estimation of out of sample errors* 
```{r}
RFPred <- predict(model, testing, type = "class")
confusionMatrix(RFPred, testing$classe)
```

*Prediction of the Results*
```{r}
RFPrediction <- predict(model, test, type = "class")
RFPrediction
```
